### 2020-10-13 latex/vnhcs.tex
Fixed a typo iin the summary of VNHCs

Finally, we saw the benefit of using VNHCs is that they reduce the
dimensionality of the system from \(2n\) equations of motion to \(2(n-k)\)
equations significantly reduces the complexity of analyzing large systems.
In particular, if the system has degree of underactuation one, the dynamics
reduce to a \(2\)D system on the ``\((q,p)\)-plane" \(\Rt{T}\times\R\).

>>>>

Finally, we saw the benefit of using VNHCs is that they reduce the
dimensionality of the system from \(2n\) equations of motion to \(2(n-k)\)
equations, which significantly reduces the complexity of analyzing large systems.
In particular, if the system has degree of underactuation one, the dynamics
reduce to a \(2\)D system on the ``\((q,p)\)-plane" \(\Rt{T}\times\R\).
